---
title: "GEOQuery Data Exploration: Neural Constructs"
output: html_notebook
---

The purpose of this script is to extract the metadata from GEOQuery in order to link GEO Ids to sample metadata/relevant information. This metadata will be used in further machine leaarning applications and Differential gene expression analysis. 

```{r}

library(dplyr)
library(tidyverse)
library(GEOquery)
```

```{r}
gse <- getGEO(GEO = 'GSE63935', GSEMatrix = TRUE)
```
```{r}
gse
```
```{r}

metadata <- pData(phenoData(gse[[1]])) #First object of the first element in the list. 
metadata
```


```{r}
#Select rows of interest I am only interested in day 16 and day 21 samples. These occur in rows 16:303 of the metadata daaframe
#Select columns of interest. I need Geo accession column, screening chemicals:ch1,title, and relation.1
metadata.modified <- metadata[16:303,]

```
```{r}
#Successfully selected rows of interest from days 16 and 21
dim(metadata.modified)
```


```{r}
metadata.modified<- metadata.modified  %>%
  rename(SRAsample=relation.1 ) %>%
  mutate(SRAsample= gsub("SRA: https://www.ncbi.nlm.nih.gov/sra?term=", "", SRAsample)) 
```
```{r}
head(metadata.modified)
```

```{r}
SRR_ID_day16_day21<-metadata.modified$geo_accession
```
```{r}
SRR_ID_day16_day21
```
Now, make two separate lists of IDs in order to filter day 16 and day 21 samples separately.
Day 16 samples are rows 1:144 of metadata.modified, Day 21 samples are rows 145:288
```{r}
metadata.modified
```
```{r}
day_16_ID<-rownames(metadata.modified[1:144,])
```


```{r}
head(day_16_ID)
```

```{r}
day_21_ID<-rownames(metadata.modified[145:288,])
```

```{r}
day_21_ID
```
```{r}
#Check if both lists are of the same dimensions (they should be)
length(day_21_ID)==length(day_16_ID)
```






